The pollination trade-off

### 2018-12-09 paper/manuscript.Rmd
Minor edits to results
Close #51

We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship or a between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others. 
Furthermore, although there was wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

We tested two random structures. 
As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).

@@

We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
However, the difference between the coefficient that relates visit effectiveness to heterospecific and conspecific pollen deposition suggests a negative, but marginal, relationship of this variable and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination. 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).

```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**. (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen. Meanwhile, the number of shared pollinators was relatively unimportant. The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen. Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association. The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel). Results are only shown for models that included explanatory variable. (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination. The plot shows the model averaged mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
height1 <- 1
height2 <- 1.29
# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/5*2
mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)

@@

We used a PCA of the analysed species to investigate whether plants strategy are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
The first component was dominated by changes on the visit effectiveness and the relative abundance while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other. 
Indeed, when we measured the median distance between the plants coordinates we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).

>>>>

We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
We found that the overall slope of the relationship was positive (Table SXX), but a large proportion of plants experienced a negative or no significant relationship between heterospecific and conspecific pollen (`r counts_facilitation_slope$np[1]`% and `r counts_facilitation_slope$np[2]`% respectively; Figure \@ref(fig:fig-trade-off-predictions)a). 
Most of the variation between plants in a facilitation-competition gradient was driven by differences *between* species, however, we also observed some important differences *within* species. 
For instance, `r numbers2words(nrow(sp_both_pos_neg))` of species sampled in multiple communities (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed evidence that facilitation (positive relationships) predominates in some communities while competition (negative relationships) predominates in others. 
Furthermore, although there was a wide variation in the slope of the relationship between heterospecific and conspecific pollen, plants, in almost all cases, had more conspecific than heterospecific pollen deposited on their stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

@@

We tested two structures for the random effects. 
As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).

@@

We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
This is, factors that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
However, the mean of the coefficients that relates visit effectiveness to heterospecific pollen deposition is slightly larger than that of conspecific pollen. 
This suggest a negative, albeit marginal, relationship of visit effectiveness and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination. 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to all other ecological factors. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).

```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="**Effect of ecological factors in the pollination service**. (a) The plant's visit effectiveness and relative abundance are the most important variables determining the deposition of conspecific and heterospecific pollen. Meanwhile, the number of shared pollinators was relatively unimportant. The graph shows the relative variable importance calculated as the sum of the Akaike weights of the candidate models that included the variable. (b) The association of ecological variables on heterospecific pollen tended to be aligned with its association on conspecific pollen. Visit effectiveness and functional originality had a positive association with pollen deposition, while abundance and the number of shared pollinators had a negative association. The plot shows the distribution of the effects (across 99 bootstrap replicates) of the four ecological variables for conspecific (top panel) and heterospecific pollen (bottom panel). Results are only shown for models that included explanatory variable. (c) The end result of these associations is that only the plants' functional originality has a positive impact on both the quantity and quality of pollination. The plot shows the model averaged mean effect (± SE) of the four analysed ecological variables in the quantity and quality of pollination."}
height1 <- 1
height2 <- 1.29
# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/5*2
mult <- 2.455 # for 2/3 is xx, for 3/5 is 2.355
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)

@@

We used a PCA of the analysed species to investigate whether plants strategies are similar across communities or whether they are flexible, and therefore able to adapt to the community context. 
The first two PCA components explained `r round(this_pca$eig[2, 3])`% of the total variance (Figure \@ref(fig:fig-pca)a). 
The first component was dominated by changes in the visit effectiveness and the relative abundance, while the second component was dominated by the number of shared pollinators and the plant's functional originality. 
When we locate the species that were sampled in more than one community in the first two PCA components (Figure \@ref(fig:fig-pca)b), we observe that the strategies of a species do not seem to be close to each other. 
Indeed, when we measured the median distance between the plants coordinates, we found that it was significantly smaller than that of randomisations for only one of all analysed species (Figure \@ref(fig:fig-pca)c).
